Count pages completed in each year

### 2024-06-22 src/count_completed.Rmd
Fixed duplicate file names

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(length(old_link) > 0) %>%
    select(yr, old_link) %>%
    print
  cat("\n\n")
}
```

@@

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(length(old_link) == 0) %>%
    select(yr, old_link) %>%
    print
  cat("\n\n")
}
```

>>>>

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(nchar(old_link) > 0) %>%
    select(yr, old_link) %>%
    print
  cat("\n\n")
}
```

@@

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(nchar(old_link) == 0) %>%
    select(yr, fn, old_link) %>%
    print
  cat("\n\n")
}
```
